### 2025-01-03 documentation/supplement.tex
A few more typos fixed; text streamlined

\subsection{Parts and bill of materials}
All custom metal pieces are parts of the CAD assembly of the microscope. Ours were manufactured from aluminium stock in the university machine shop. Aluminium has the added benefit of anodization, which can help control scattered light. An overview of the microscope's cost is shown in Tab.~\ref{tab_costs}. Keep in mind that these prices can significantly change over time, while some products can become unobtainable and need to be replaced with a different or newer model.
%
\begin{table}
\begin{center}
  \begin{tabular}{ l c r } \hline
   \textbf{Item} & \textbf{Info} & \textbf{Cost} \\ \hline
\rowcolor{gray!20} 920 nm fs-pulsed Laser  & Spark Alcor 920 + Warranty & 90 k \\
                   ScanImage DAQ-System \& optimized PC & MBF Bioscience& 20 k \\
\rowcolor{gray!20} Piezo collar & Physik Instrumente & 16 k	\\
            $2\times$ PMTs + preamplifiers  & Hamamatsu \& Thorlabs & 12 k \\
\rowcolor{gray!20} Pockels cell             & Conoptics &	11 k \\
                   Objective                & Nikon &  8 k \\
\rowcolor{gray!20} Machining custom parts   & Machine Shop; as per CAD files &  7 k \\
                   Optical filters          & AVR optics \& Semrock &  7 k \\
\rowcolor{gray!20} Lenses + optomechanics   & Thorlabs \& Newport &  7 k \\
                   Galvo-Resonant Scanner set & Novanta &  6 k \\
\rowcolor{gray!20} Electronics/cables/tools & Newark \& McMaster &  5 k \\
                   Mounting rack            & Emcor Enclosures &  3 k \\
\rowcolor{gray!20} Laser shutter            & Uniblitz/Vincent &  2 k \\
                   Laser safety goggles     & Edmund Optics &  1 k \\
\rowcolor{gray!20} Laser power meter        & Coherent &  1 k \\
                   Agarose \& fluorescent beads     & Thermofisher &  1 k \\
  \hline
 \textbf{Total}                    & & \textbf{197 k} \\
  \hline
  \end{tabular}
\end{center}
\caption{\textbf{Overview of the approximate cost in 2024-US\$} Note that this list excludes the optical table, and any other infrastructure costs such as compressors for air, and associated power supplies. This is just a summary. The detailed bill of materials is provided in the git repository.}\label{tab_costs}
\end{table}

\subsection{Structure and use of this document}
In the following sections, we will cover the setup and alignment of the microscope. This is split into three parts. The first part covers all components on the optical table that serve to condition the beam. The second part focuses on the  95 mm vertical post that holds the scanning mirror and scan lens assemblies. The third part is the microscope head with the attached collection optics. We will begin with the assembly on the optical table. All along, we assume the reader will have downloaded and opened the CAD model as we will rely heavily on it. Further, check carefully the instruction manuals of the scanning mirrors, photomultiplier tubes (PMTs), power supplies, Pockels cell, ScanImage, the Piezoelectric objective collar, and the filter mounting instructions.\newline
Before building your own microscope, read these instructions fully. Check the CAD files, and make sure that the instructions make sense. This document follows closely our own alignment procedure, and we have done our best to be accurate. However, use common sense. Do not follow these instructions blindly (or you will follow these instructions blindly). Like all open instrumentation (under CC-BY-4.0), this work is distributed in the hope that it will be useful, but WITHOUT ANY WARRANTY, to the extent permitted by law; without even the implied warranty of MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.

@@

    \item \textbf{G)} Pockels cell (350-80-LA-02 with 302RM driver, Conoptics) sitting on a holder (M102A, Conoptics). Properties of light travelling through this device are controlled electrically through the two connected wires. The alignment of the Pockels cell requires two steps: The Pockels cell has to be aligned with the optical axis of the laser, and be rotated relative to the laser's polarization such that the dynamic range is maximized \cite{Conoptics2018, Scientifica2024}. The first step can be done with an alignment tool of identical geometry to the Pockels cell (Conoptics modulator alignment tool 103). The second step requires the Pockels cell to be connected, and a power measurement performed. Importantly, these steps have to be done under full power because the beam profile in alignment mode might be slightly different from the full beam.
    \begin{itemize}
        \item First, install the holder on the table, and position on it the Conoptics Pockels cell alignment tool (Conoptics modulator alignment tool 103).
        \item Use a power meter on the output side, maximize power going through the central bore by manipulating the 4 bottom screws on the holder.
        \item Then switch the laser to full power and optimize the position of the screws for maximum transmission.
        \item Tighten the screws around the alignment tool, and mark on the screws the optical position. This will be important later to reproduce the exact same position of the alignment tool with the Pockels cell.
        \item Connect the Pockels cell (M350-80-LA, Conoptics) to the driver as per the Conoptics instructions (p1m and p2m go to J1m and J2m, p1 and p2 go to the controller). The controller settings are shown in Fig.~\ref{sfig2}.
        %
        \begin{SCfigure}
            \includegraphics[width=.75\textwidth]{sfig2.jpg}
          \caption{{\bf Settings on the Pockels Cell controller.} Shown are the controls of the Pockels Cell driver as set in our system. For reference, see \cite{Conoptics2018}. We recommend for people building a microscope to take many such pictures of all settings and elements.}
          \label{sfig2}
        \end{SCfigure}
        %
        \item Next, determine the best orientation of the Pockels cell, by measuring the controller's voltage for different Pockels cell rotations. For each rotation of the Pockels cell, measure its transmission while turning the dial on the Conoptics controller from one end to the other. Iterate this for different orientations of the Pockels cell until an optimum is found. An example of different transmission curves is shown in the main manuscript, Fig. 9A. The optimal orientation allows to adjust the laser power in the widest range.
        \item The Pockels Cell splits the input beam into a transmitted and a rejected beam. The transmitted beam is used, while the energy of the rejected beam is dissipated in a beam block. By changing the control voltage of the Pockels Cell, the power ratio between the transmitted and rejected beam can be adjusted. The rejected beam leaves the Pockels cell through a bore at its side. During alignment, make sure that the rejected beam is properly terminated with a beam block.
        \item To validate the alignment, compute the extinction ratio of the Pockels cell, i.e. the ratio of maximal and minimal light transmission, and compare that number with the data sheet provided by Conoptics. Ours operate in a regime of $\approx 450$.
        \item Next, set the Pockels cell controller to the control voltage corresponding to minimum light transmission.
        \item Tighten the holder, and confirm that the Pockels cell is still well-aligned.
    \end{itemize}

@@

Following beam conditioning on the optical table, the beam is reflected up from the optical table towards the ceiling into a box housing the scanning mirrors. This is shown in Fig.~\ref{sfig4}A,B. Following the scanning mirrors, the beam travels up through the scan lens, and directed to the microscope head with another mirror.
%
\begin{figure}[h]
    \includegraphics[width=\textwidth]{sfig4.jpg}
    \caption{{\bf Overall view of the scanning post.} \textbf{A)} Side few. Key components of the system are labeled with capital letters. These are explained in the text together with a note on how to align these components. Importantly, the machined block (C) houses the scanning mirrors, and the scan lens assembly is placed in the SM2 house labeled (E). \textbf{B)} Frontal view. The PMT preamplifiers (component G) and the scanning mirror power supply (component H) are visible.}
    \label{sfig4}
\end{figure}
%
%
\begin{enumerate}[]
    \item \textbf{A)} Mirror (PF10-03-P01, inside KCB1, with CP12 attached) - turn the beam at a right angle.
    \item \textbf{B)} Broadband filter (WG11010-B, Thorlabs, inside SM1L20 and SM1S20) - filter to keep dust out of the box housing the scanning mirrors.
    \item \textbf{C)} An aluminium box containing the resonant and slow galvanometer set (CRS8K/6215H Resonant-Galvo Set, Novanta), mounted to 95 mm rail (XT95RC4, Thorlabs). A detailed description is provided below.
    \item \textbf{D)} Empty tubing (SM2V05, adjustable SM2 Lens Tube, Thorlabs).
    \item \textbf{E)} Scan lens - See detailed description below.
    \item \textbf{F)} Mirror in its housing (PF20-03-P01 and KCB2, both Thorlabs). While we used a round 2 inch mirror, this should be replaced with an elliptical mirror and housing (PFE20-P01 and KCB2EC, both Thorlabs). This would increase the field-of-view because the cross-section of an ellipse at 45 degrees is a circle. At low magnification, a round mirror will lead to vignetting.
    \item \textbf{G)} PMT preamplifier (TIA60, Thorlabs) attached to a 95 mm rail.
    \item \textbf{H)} Power supply for the scanning mirrors (part of the Novanta scanning mirror set) housed in an electronics prototype box.
\end{enumerate}

@@

\begin{itemize}
    \item First, mount the 95 mm rail to the table. Then attach a bracket (all from the XT95 series, Thorlabs) to the side to hold the scan lens (component D in Fig.~\ref{sfig3}), and one on top with a cage system to hold a mirror (component F in Fig.~\ref{sfig3}). For alignment with cage systems, we use a cage system alignment plate (VRC4CPT, Thorlabs). The rest of the assembly here will be done without any lenses. The goal is a well-aligned beam that travels through the center of all parts, and parallel to the optomechanical surfaces.
    \item The box housing the scanning mirrors is connected, trough SM1 tubing, to a mirror (component A in Fig.~\ref{sfig3}). To align this upper periscope mirror with the lower periscope mirror, mounted on the table, connect a piece of SM1 tubing to the upper mirror facing down, and  a second piece of SM1 tubing to the table mirror facing up (component M in Fig.~\ref{sfig1}). These two pieces meet in mid-air. The gap in between can be reduced to zero using adjustable length SM1 lens tube (e.g. SM1V10, Thorlabs, not shown in CAD) and can be further closed by a small portion of  lens tube cover (SC600, Thorlabs). 
    \item Next, we adjust the mirror (component A in Fig.~\ref{sfig4}A) so that light travels through the center of the scanning mirrors and up the 95 mm rail. This is done with irises. One is attached at the entry port of the scanning mirror box, e.g. in the SM1 tube (component B in Fig.~\ref{sfig4}A). Another two irises are attached, as far away as possible, to a 95 mm rail bracket. It is convenient to use the future holder of the scan lens (component D/E in Fig.~\ref{sfig4}). This ensures that the beam will pass through the center of the scan lens. As the mirror (component F in Fig.~\ref{sfig4}) is not installed yet, an IR detection card can conveniently be taped to the ceiling to make sure that the beam is on-axis. Of note, the resonant scanner is at its origin point when no power is being provided, but the slow galvanometer needs to be provided 0 Volt to position the mirror at its origin point. This can be done through the voltage supply, or to a good approximation through ScanImage by setting the scan mode to the highest possible zoom level. In our microscope design, it can be helpful to wiggle the lid to which the scanning mirrors are mounted (item C in Fig.~\ref{sfig4}). This step is tricky and can require some patience. 
    \item When confirmed that the light travels parallel to the 95 mm rail, we attach the mirror (component F in Fig.~\ref{sfig4}), and slide it along the cage rods to a position where the beam is reflected centrally through the caging system and the mount positioned on top of the 95 mm rail. This is done using the same set of two SM2-mounted irises that we used to make sure that light leaves the scanning mirror box without x or y displacement. The beam is now ready to travel through the microscope head.
\end{itemize}

@@

\subsubsection{PMT installation}
PMTs are light sensitive. Always store them with their aperture covered with blackout tape when not in use (AT205-1.0 black aluminium foil tape, Thorlabs). When removing the tape for installation, this installation into the collection box must be done in darkness and as quickly as possible. We recommend to use black silicone putty (V-tie self setting silicone rubber), and have it ready for use to seal the gap between the PMTs and the aluminium box. Switch the room lights off, wait a few minutes to adapt to the darkness then mount the PMTs on their respective ports. Of note, when ordering the PMTs from Hamamatsu, one can request PMTs with particularly low dark count to reduce noise.

@@

    \item Finally, use a fluorescent bead sample to measure the microscope's point spread function (PSF), see Fig.~\ref{sfig7}C. This will reveal more subtle misalignment and aberration in the optics. We use a mix of 5000:1 100 nm fluorescent beads (``Dragon Green'' 480/520 from Bangs Laboratories) in in 1\% Agarose. To prepare this sample, take the beads from the fridge, vortex the container, take the 10 \textmu l and 49.5 g of water. Then microwave the mix with 0.5 g of Agarose until the solution is clear. While warm, place a drop on a microscope slide, and cover with a coverslip. Bring your sample to the microscope, and record a z-stack. Use low laser power to not damage the bead, or saturate the PMTs. The example shown was recorded with 5\% laser power at 99.9 zoom for 40 z-slices with 0.5 \textmu m spacing. The PSF profile should be symmetric, and a faint, but also symmetric, Airy ring visible around the bead, around 5 \textmu m away from center of the bead (see Fig. 2D in the main manuscript).

@@

    \item \textbf{B)} Next, we attach the front panel. This is connected  with stainless steel Phillips flat head screws, 82 degree countersink angle, 4-40 Thread, 1/8 in long and undercut.

@@

    \item \textbf{F)} Next, we fix the condenser lenses (ACL25416U-A, Thorlabs) in their housing plates. The convex part is facing towards the inside of the box, and set with nylon set screws (Stainless Steel Nylon-Tip Set Screw, 4-40 Thread, 1/8 inch long). The holders are then fixed together with stainless steel socket head screw, 8-32 thread size, 3/8 inch long.
    \item \textbf{G)} With the condensers in place, we can install the optical band-pass filters in front of them. First the 525 nm band-pass filter (Semrock Brightline FF01-525/45-32, AVR Optics) for the green channel, which is secured with a nylon set screw (stainless steel nylon-tip set screw, 4-40 thread, 1/8 inch long). Orientation is important: For this brand of filters, the arrow is following the light path, i.e. away from the inside of the box and towards the PMT.

@@

    \item \textbf{K)} The bottom piece (bottom per the view of the picture in Fig.~\ref{sfig9}B) of the PMT box is attached using 4-40, undercut, 3/16 inch screws.
    \item \textbf{L)} PMT plate. The PMT attaches to the flat side of the PMT plates with 4 specialized low profile screws (CBSTSR2-6, Misumi). The other side has a shallow cut out for the screw head to sit. The plate with the PMT attached screws into the rest of the assembly using 4-40 5/16 inch, socket cap screws.

@@

    \item \textbf{N)} Then we close the second panel with 8/32, 1/2 inch, socket cap screws.

@@

    \item \textbf{P)} The lid is attached using 8/32, 3/8 inch, undercut screws. Finish off by securing the rest of the front plate screws (component B) using 4-40 thread, 1/8 inch screws. Screw in the piece holding M to the lid using 4-40, 1/2 inch, socket cap screws.
    \item \textbf{Q)} Attach the top cover using 4-40, undercut, 3/16 inch screws.

@@

    \caption{{\bf The scanning mirror box.} \textbf{A)} The custom aluminium box housing the pair of scanning mirrors. \textbf{B)} Close-up of the same box with key parts labeled: A: Two windows (WG11010-B, Thorlabs) to keep dust out. B: Attachment of the box to the 95 mm optical rail. C: An Iris used for alignment, and D: SM1 tubing. \textbf{C)} Bottom part of the aluminium box. A: the windows, and B: screws to attach the box to the drop-on rail carriage via four 0.75 inch tall 1 inch diameter posts. \textbf{D)} The scanning mirrors are mounted to the lid using heat transfer compound. E: Anodized aluminium block holding the scanning mirrors. F: One of the scanning mirror assemblies, G: The aluminium lid and H: The scanning mirrors. \textbf{E)} Same as \textbf{D} but different angle. \textbf{F)} Same as \textbf{E} but different angle. I: Cables controlling the scanning mirrors.}

@@

\textcolor{blue}{To provide these three signals, we used a power supply with two galvanically isolated and adjustable output channels, that can be connected in series (Note: not every power supply can do this. We used a GPD-3303D from Gw Instek that allows this function with the SER/INDEP key). The voltage of each of the two unconnected channels was set to +28 V. To produce the three supply signals, we used these two channels in series. In other words, we connect the positive terminal of the first channel to the negative terminal of the second channel. As the channels are otherwise not connected to a common ground (this is meant with the words ``galvanically isolated''), this does not produce a short circuit. Instead, this link effectively provides a new reference point, relative to which the first supply produces a negative -28 V supply, and the second supply produces the +28 V supply. This is illustrated in Fig.~\ref{sfig11}C. In this arrangement, a multimeter would read between points G and I +28 V, between G and F -28 V, and between F and I +56 V. The supply of the resonant scanners is simpler, as it only requires a single +12 V line. The supplies are connected to the power supply ports on the prototype box, in which the two driver boards reside, see Fig.~\ref{sfig11}D. Signal lines are connected on the outside with coaxial cables to the MBF Bioscience DAQ system, see Fig.~\ref{sfig11}E.} Key components in the panels are labeled with capital letters. These are as follows:

@@

    \item Solder 2.5 inch long, and 5 inch long pieces of wires to pin 12 on the top display.
    \item Solder the other end of the 2.5 inch piece of wire and a new 1 inch piece of wire to pin 3 (+5 V return).
    \item Solder the other end of the 1 inch piece of wire and a 1.5 inch and 3 inch pieces to display pin 6 (DP1).
    \item Solder the other end of the 1.5 inch piece and another 1 inch piece to pin 3 (+5 V return) of the bottom display.
    \item Solder the other end of the 1 inch piece and a new 2 inch piece to pin 6 (DP1) of the bottom display.
    \item Solder the other end of the 2 inch piece to pin 12 (input lo) of the bottom display.
    \item Solder the other end of the 3 inch piece from pin 6 (DP1) of the top display and a new 12 inch piece of wire to the middle pin of the left potentiometer.
    \item Solder a 12 inch piece of wire to pin 3 (closest to the knob) on the left potentiometer (50 kOhm, 3590S-1-503L, Bourns). These are the two big blue parts, component \textbf{B}, in Fig.~\ref{sfig12}A,B.
    \item Solder a 12 inch piece of wire and 5 inch piece of wire to pin 11 (input hi) on the top display.

>>>>

\subsection{Parts and bill of materials}
All custom metal pieces are parts of the CAD assembly of the microscope. Ours were manufactured from aluminium stock in the university machine shop. Aluminium has the added benefit of anodization, which can help control scattered light. An overview of the microscope's cost is shown in Tab.~\ref{tab_costs}. Keep in mind that these prices can significantly change over time, while some products can become unobtainable and need to be replaced with a different or newer model.
%
\begin{table}
\begin{center}
  \begin{tabular}{ l c r } \hline
   \textbf{Item} & \textbf{Info} & \textbf{Cost} \\ \hline
\rowcolor{gray!20} 920 nm fs-pulsed Laser  & Spark Alcor 920 + Warranty & 90 k \\
                   ScanImage DAQ-System \& optimized PC & MBF Bioscience& 20 k \\
\rowcolor{gray!20} Piezo collar & Physik Instrumente & 16 k	\\
            $2\times$ PMTs + preamplifiers  & Hamamatsu \& Thorlabs & 12 k \\
\rowcolor{gray!20} Pockels cell             & Conoptics &	11 k \\
                   Objective                & Nikon &  8 k \\
\rowcolor{gray!20} Machining custom parts   & Machine Shop; as per CAD files &  7 k \\
                   Optical filters          & AVR optics \& Semrock &  7 k \\
\rowcolor{gray!20} Lenses + optomechanics   & Thorlabs \& Newport &  7 k \\
                   Galvo-Resonant Scanner set & Novanta &  6 k \\
\rowcolor{gray!20} Electronics/cables/tools & Newark \& McMaster &  5 k \\
                   Mounting rack            & Emcor Enclosures &  3 k \\
\rowcolor{gray!20} Laser shutter            & Uniblitz/Vincent &  2 k \\
                   Laser safety goggles     & Edmund Optics &  1 k \\
\rowcolor{gray!20} Laser power meter        & Coherent &  1 k \\
                   Agarose \& fluorescent beads     & Thermofisher &  1 k \\
  \hline
 \textbf{Total}                    & & \textbf{197 k} \\
  \hline
  \end{tabular}
\end{center}
\caption{\textbf{Overview of the approximate cost in US-\$ (2024).} Note that this list excludes the optical table, and any other infrastructure costs such as compressors for air, and associated power supplies. This is just a summary. The detailed bill of materials is provided in the git repository.}\label{tab_costs}
\end{table}

\subsection{Structure and use of this document}
In the following sections, we will cover the setup and alignment of the microscope. This is split into three parts. The first part covers all components on the optical table that serve to condition the beam. The second part focuses on the  95 mm vertical post that holds the scanning mirror and scan lens assemblies. The third part is the microscope head with the attached collection optics. We will begin with the assembly on the optical table. All along, we assume the reader will have downloaded and opened the CAD model as we will rely heavily on it. Further, check carefully the instruction manuals of the scanning mirrors, photomultiplier tubes (PMTs), power supplies, Pockels cell, ScanImage, the Piezoelectric objective collar, and the filter mounting instructions.\newline
Before building your own microscope, read these instructions fully. Check the CAD files, and make sure that the instructions make sense. This document follows closely our own alignment procedure, and we have done our best to be accurate. However, use common sense. Do not follow these instructions blindly (or you might follow these instructions blindly). Like all open instrumentation (under CC-BY-4.0), this work is distributed in the hope that it will be useful, but WITHOUT ANY WARRANTY, to the extent permitted by law; without even the implied warranty of MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.

@@

    \item \textbf{G)} Pockels cell (350-80-LA-02 with 302RM driver, Conoptics) sitting on a holder (M102A, Conoptics). Properties of light travelling through this device are controlled electrically through the two connected wires. The alignment of the Pockels cell requires two steps: The Pockels cell has to be aligned with the optical axis of the laser, and be rotated relative to the laser's polarization such that the dynamic range is maximized \cite{Conoptics2018, Scientifica2024}. The first step can be done with an alignment tool of identical geometry to the Pockels cell (Conoptics modulator alignment tool 103). The second step requires the Pockels cell to be connected, and a power measurement performed. Importantly, these steps have to be done under full power because the beam profile in alignment mode might be slightly different from the full beam.
    \begin{itemize}
        \item First, install the holder on the table, and position on it the Conoptics Pockels cell alignment tool (Conoptics modulator alignment tool 103).
        \item Use a power meter on the output side, maximize power going through the central bore by manipulating the 4 bottom screws on the holder.
        \item Then switch the laser to full power and optimize the position of the screws for maximum transmission.
        \item Tighten the screws around the alignment tool, and mark on the screws the optical position. This will be important later to reproduce the exact same position of the alignment tool with the Pockels cell.
        \item Connect the Pockels cell (M350-80-LA, Conoptics) to the driver as per the Conoptics instructions (\texttt{p1m} and \texttt{p2m} go to \texttt{J1m} and \texttt{J2m}, \texttt{p1} and \texttt{p2} go to the controller). The controller settings are shown in Fig.~\ref{sfig2}.
        %
        \begin{SCfigure}
            \includegraphics[width=.75\textwidth]{sfig2.jpg}
          \caption{{\bf Settings on the Pockels Cell controller.} Shown are the controls of the Pockels Cell driver as set in our system. For reference, see \cite{Conoptics2018}. We recommend for people building a microscope to take many such pictures of all settings and elements.}
          \label{sfig2}
        \end{SCfigure}
        %
        \item Next, determine the best orientation of the Pockels cell: For several rotations of the Pockels cell, measure its transmission while turning the dial on the Conoptics controller from one end to the other. Iterate this for different orientations of the Pockels cell until an optimum is found at which the dynamic range is greatest. This optimal orientation allows to adjust the laser power in the widest range. An example of different transmission curves is shown in the main manuscript, Fig. 9A. 
        \item The Pockels Cell splits the input beam into a transmitted and a rejected beam. The transmitted beam is used, while the energy of the rejected beam is dissipated in a beam block. By changing the control voltage of the Pockels Cell, the power ratio between the transmitted and rejected beam can be adjusted. The rejected beam leaves the Pockels cell through a bore at its side. During alignment, make sure that the rejected beam is properly terminated with a beam block.
        \item To validate the alignment, compute the extinction ratio of the Pockels cell, i.e. the ratio of maximal and minimal light transmission, and compare that number with the data sheet provided by Conoptics. Ours operate in a regime of $\approx 450$.
        \item Next, set the Pockels cell controller to the control voltage corresponding to minimum light transmission.
        \item Tighten the holder, and confirm that the Pockels cell is still well-aligned.
    \end{itemize}

@@

Following beam conditioning on the optical table, the beam is reflected up from the optical table towards the ceiling into a box housing the scanning mirrors. This is shown in Fig.~\ref{sfig4}A,B. Following the scanning mirrors, the beam travels up through the scan lens, and directed to the microscope head with another mirror.
%
\begin{figure}[h]
    \includegraphics[width=\textwidth]{sfig4.jpg}
    \caption{{\bf Overall view of the scanning post.} \textbf{A)} Side few. Key components of the system are labeled with capital letters. These are explained in the text together with a note on how to align these components. Importantly, the machined block (C) houses the scanning mirrors, and the scan lens assembly is placed in the SM2 house labeled (E). \textbf{B)} Frontal view. The PMT preamplifiers (component G) and the scanning mirror power supply (component H) are visible.}
    \label{sfig4}
\end{figure}
%
%
\begin{enumerate}[]
    \item \textbf{A)} Mirror (PF10-03-P01, inside KCB1, with CP12 attached) - turn the beam at a right angle.
    \item \textbf{B)} Broadband filter (WG11010-B, Thorlabs, inside SM1L20 and SM1S20) - filter to keep dust out of the box housing the scanning mirrors.
    \item \textbf{C)} An aluminium box containing the resonant and slow galvanometer set (CRS8K/6215H Resonant-Galvo Set, Novanta), mounted to 95 mm rail (XT95RC4, Thorlabs). A detailed description is provided below.
    \item \textbf{D)} Empty tubing (SM2V05, adjustable SM2 Lens Tube, Thorlabs).
    \item \textbf{E)} Scan lens - See detailed description below.
    \item \textbf{F)} Mirror in its housing (PF20-03-P01 and KCB2, both Thorlabs). While we used a round $\diameter2\text{ inch}$ mirror, this should be replaced with an elliptical mirror and housing (PFE20-P01 and KCB2EC, both Thorlabs). This would increase the field-of-view because the cross-section of an ellipse at 45 degrees is a circle. At low magnification, a round mirror will lead to vignetting.
    \item \textbf{G)} PMT preamplifier (TIA60, Thorlabs) attached to a 95 mm rail.
    \item \textbf{H)} Power supply for the scanning mirrors (part of the Novanta scanning mirror set) housed in an electronics prototype box.
\end{enumerate}

@@

\begin{itemize}
    \item First, mount the 95 mm rail to the table. Then attach a bracket (all from the XT95 series, Thorlabs) to the side to hold the scan lens (component D in Fig.~\ref{sfig3}), and one on top with a cage system to hold a mirror (component F in Fig.~\ref{sfig3}). For alignment with cage systems, we use a cage system alignment plate (VRC4CPT, Thorlabs). The rest of the assembly here will be done without any lenses. The goal is a well-aligned beam that travels through the center of all parts, and parallel to the optomechanical surfaces.
    \item The box housing the scanning mirrors is connected, trough SM1 tubing, to a mirror (component A in Fig.~\ref{sfig3}). To align this upper periscope mirror with the lower periscope mirror, mounted on the table, connect a piece of SM1 tubing to the upper mirror facing down, and  a second piece of SM1 tubing to the table mirror facing up (component M in Fig.~\ref{sfig1}). These two pieces meet in mid-air. The gap in between can be reduced to zero using adjustable length SM1 lens tube (e.g. SM1V10, Thorlabs, not shown in CAD) and can be further closed by a small piece of  lens tube cover (SC600, Thorlabs). 
    \item Next, we adjust the mirror (component A in Fig.~\ref{sfig4}A) so that light travels through the center of the scanning mirrors and up the 95 mm rail. This is done with irises. One is attached at the entry port of the scanning mirror box, e.g. in the SM1 tube (component B in Fig.~\ref{sfig4}A). Another two irises are attached, as far away as possible, to a 95 mm rail bracket. It is convenient to use the future holder of the scan lens (component D/E in Fig.~\ref{sfig4}). This ensures that the beam will pass through the center of the scan lens. As the mirror (component F in Fig.~\ref{sfig4}) is not installed yet, an IR detection card can conveniently be taped to the ceiling to make sure that the beam is on-axis. Of note, the resonant scanner is at its origin point when no power is being provided, but the slow galvanometer needs to be provided 0 V to position the mirror at its origin point. This can be done through the voltage supply, or to a good approximation through ScanImage by setting the scan mode to the highest possible zoom level. In our microscope design, it can be helpful to wiggle the lid to which the scanning mirrors are mounted (item C in Fig.~\ref{sfig4}). This step is tricky and can require some patience. 
    \item When confirmed that the light travels parallel to the 95 mm rail, we attach the mirror (component F in Fig.~\ref{sfig4}), and slide it along the cage rods to a position where the beam is reflected centrally through the caging system and the mount positioned on top of the 95 mm rail. This is done using the same set of two SM2-mounted irises that we used to make sure that light leaves the scanning mirror box without x or y displacement. The beam is now ready to travel through the microscope head.
\end{itemize}

@@

\subsubsection{PMT installation}
PMTs are light sensitive. Always store them with their aperture covered with blackout tape when not in use (AT205-1.0 black aluminium foil tape, Thorlabs). When removing the tape for installation, this installation into the collection box must be done in darkness and as quickly as possible. We recommend to use black silicone putty (V-tie self setting silicone rubber), and have it ready for use to seal the gap between the PMTs and the aluminium box. Switch the room lights off, wait a few minutes to adapt to the darkness then mount the PMTs on their respective ports. Of note, when ordering the PMTs from Hamamatsu, one can request PMTs with particularly low dark count and high quantum efficiency to reduce noise. We typically request a quantum efficiency of at least 45\% at 520 nm, and a dark count of 4000 cps or below at 25 degree Celcius.

@@

    \item Finally, use a fluorescent bead sample to measure the microscope's point spread function (PSF), see Fig.~\ref{sfig7}C. This will reveal more subtle misalignment and aberration in the optics. We use a 5000:1 mix of 100 nm fluorescent beads (``Dragon Green'' 480/520 from Bangs Laboratories) in in 1\% Agarose. To prepare this sample, take the beads from the fridge, vortex the container, take the 10 \textmu l and 49.5 g of water. Then microwave the mix with 0.5 g of Agarose until the solution is clear. While warm, place a drop on a microscope slide, and cover with a coverslip. Bring your sample to the microscope, and record a z-stack. Use low laser power to not damage the beads, or saturate the PMTs. The example shown was recorded with 5\% laser power at 99.9 zoom for 40 z-slices with 0.5 \textmu m spacing. The PSF profile should be symmetric, and a faint, but also symmetric, Airy ring visible around the bead, around 5 \textmu m away from center of the bead (see Fig. 2D in the main manuscript).

@@

    \item \textbf{B)} Next, we attach the front panel. This is connected  with stainless steel Phillips flat head screws, 82 degree countersink angle, 4-40 thread size, 1/8 inch long and undercut.

@@

    \item \textbf{F)} Next, we fix the condenser lenses (ACL25416U-A, Thorlabs) in their housing plates. The convex part is facing towards the inside of the box, and set with nylon set screws (Stainless Steel Nylon-Tip Set Screw, 4-40 thread size, 1/8 inch long). The holders are then fixed together with stainless steel socket head screw, 8-32 thread size, 3/8 inch long.
    \item \textbf{G)} With the condensers in place, we can install the optical band-pass filters in front of them. First the 525 nm band-pass filter (Semrock Brightline FF01-525/45-32, AVR Optics) for the green channel, which is secured with a nylon set screw (stainless steel nylon-tip set screw, 4-40 thread size, 1/8 inch long). Orientation is important: For this brand of filters, the arrow is following the light path, i.e. away from the inside of the box and towards the PMT.

@@

    \item \textbf{K)} The bottom piece (bottom per the view of the picture in Fig.~\ref{sfig9}B) of the PMT box is attached using 4-40 thread size, undercut, 3/16 inch long screws.
    \item \textbf{L)} PMT plate. The PMT attaches to the flat side of the PMT plates with 4 specialized low profile screws (CBSTSR2-6, Misumi). The other side has a shallow cut out for the screw head to sit. The plate with the PMT attached screws into the rest of the assembly using 4-40 thread size, 5/16 inch long socket cap screws.

@@

    \item \textbf{N)} Then we close the second panel with 8-32 thread size, 1/2 inch long socket cap screws.

@@

    \item \textbf{P)} The lid is attached using 8-32 thread size, 3/8 inch long, undercut screws. Finish off by securing the rest of the front plate screws (component B) using 4-40 thread size, 1/8 inch long screws. Screw in the piece holding M to the lid using 4-40 thread size, 1/2 inch long socket cap screws.
    \item \textbf{Q)} Attach the top cover using 4-40 thread size, undercut, 3/16 inch long screws.

@@

    \caption{{\bf The scanning mirror box.} \textbf{A)} The custom aluminium box housing the pair of scanning mirrors. \textbf{B)} Close-up of the same box with key parts labeled: A: Two windows (WG11010-B, Thorlabs) to keep dust out. B: Attachment of the box to the 95 mm optical rail. C: An Iris used for alignment, and D: SM1 tubing. \textbf{C)} Bottom part of the aluminium box. A: the windows, and B: screws to attach the box to the drop-on rail carriage via four 3/4 inch tall $\diameter1\text{ inch}$ diameter posts. \textbf{D)} The scanning mirrors are mounted to the lid using heat transfer compound. E: Anodized aluminium block holding the scanning mirrors. F: One of the scanning mirror assemblies, G: The aluminium lid and H: The scanning mirrors. \textbf{E)} Same as \textbf{D} but different angle. \textbf{F)} Same as \textbf{E} but different angle. I: Cables controlling the scanning mirrors.}

@@

\textcolor{blue}{To provide these three signals, we used a power supply with two galvanically isolated and adjustable output channels, that can be connected in series (Note: not every power supply supports this function. We used a GPD-3303D from Gw Instek that allows this function with the SER/INDEP key). The voltage of each of the two unconnected channels was set to +28 V. To produce the three supply signals, we used these two channels in series. In other words, we connect the positive terminal of the first channel to the negative terminal of the second channel. As the channels are otherwise not connected to a common ground (this is meant with the words ``galvanically isolated''), this does not produce a short circuit. Instead, this link effectively provides a new reference point, relative to which the first supply produces a negative -28 V supply, and the second supply produces the +28 V supply. This is illustrated in Fig.~\ref{sfig11}C. In this arrangement, a multimeter would read between points G and I +28 V, between G and F -28 V, and between F and I +56 V. The supply of the resonant scanners is simpler, as it only requires a single +12 V line. The supplies are connected to the power supply ports on the prototype box, in which the two driver boards reside, see Fig.~\ref{sfig11}D. Signal lines are connected on the outside with coaxial cables to the MBF Bioscience DAQ system, see Fig.~\ref{sfig11}E.} Key components in the panels are labeled with capital letters. These are as follows:

@@

    \item Solder 2.5 inch long and 5 inch long pieces of wires to pin 12 on the top display.
    \item Solder the other end of the 2.5 inch long piece of wire and a new 1 inch long piece of wire to pin 3 (+5 V return).
    \item Solder the other end of the 1 inch long piece of wire, and add 1.5 inch and 3 inch long pieces to display pin 6 (DP1).
    \item Solder the other end of the 1.5 inch long piece and another 1 inch long piece to pin 3 (+5 V return) of the bottom display.
    \item Solder the other end of the 1 inch long piece and a new 2 inch long piece to pin 6 (DP1) of the bottom display.
    \item Solder the other end of the 2 inch long piece to pin 12 (input lo) of the bottom display.
    \item Solder the other end of the 3 inch long piece from pin 6 (DP1) of the top display and a new 12 inch long piece of wire to the middle pin of the left potentiometer.
    \item Solder a 12 inch long piece of wire to pin 3 (closest to the knob) on the left potentiometer (50 kOhm, 3590S-1-503L, Bourns). These are the two big blue parts, component \textbf{B}, in Fig.~\ref{sfig12}A,B.
    \item Solder a 12 inch long piece of wire and 5 inch long piece of wire to pin 11 (input hi) on the top display.
